Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-10 ms.tex
Update on Overleaf.

The observed phenomena of radio transients span orders of magnitude in timescales -- provide examples \citep{Pietka+2015,Chandra+2016}.

@@

We consider aperture arrays that operate interferometrically and hierarchically on multiple spatial scales. Examples of these multi-scale hierarchical aperture arrays include the Murchison Widefield Array \cite[MWA;][]{Tingay+2013}, the Low Frequency Array \cite[LOFAR;][]{vanHaarlem+2013}, the swarm of Long Wavelength Arrays \cite[LWA Swarm;][]{Dowell+2018}, and the Square Kilometre Array low \cite[SKA-low;][]{Dewdney+2009}. The specific spatial scales are the dimensions of the antenna, station (a grouping of antennas), and the array (a grouping of stations), denoted by $D_\textrm{a}$, $D_\textrm{s}$, and $D_\textrm{A}$, respectively. The number of stations in the array and the number of antennas in a station (indexed by $m$) are denoted by $N_\textrm{s}$ and $N_{\textrm{a/s}_m}$, respectively. 
% Although $N_\textrm{a/s_m}$ could vary with each station, we assume it remains the same for each station for simplicity.

@@

\begin{figure*}
\includegraphics[width=\linewidth]{figures/flops_calc.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:hybrid-architectures-cost-schematic}}
\end{figure*}

>>>>

The variable and transient radio sky encompasses a variety of intriguing astrophysical phenomena. These events occur across timescales spanning orders of magnitude, frequency ranges, and polarizations \citep[][and references therein]{Pietka+2015,Chandra+2016}. Notable examples include pulsars and their giant radio pulses, magnetars, fast radio bursts (FRBs), rotating radio transients (RRATs), Jovian and solar bursts, flare stars, cataclysmic variables (CVs), exoplanet and stellar outbursts, X-ray binaries, novae, supernovae, gamma-ray bursts (GRBs) and their afterglows, active galactic nuclei (AGNs) and blazars, tidal disruption events, both the prompt and afterglow counterparts to gravitational wave (GW) merger events, as well as many phenomena yet to be understood \citep{Lorimer+2007,Thyagarajan+2011,Keane2013,Thornton+2013,Bochenek+2020}.

The effectiveness of discovering these transients depends on an instrument's field of view and the duration of on-sky observation \citep{Cordes2007}. Ideally, instruments should operate continuously, covering a wide range of timescales from microseconds to days, with a large instantaneous field of view. However, due to the significant computational and data rate demands, compromises are often made by limiting one or more discovery parameters such as time resolution, on-sky observing time, field of view, angular resolution, or bandwidth.

@@

Modern radio arrays tend to be aperture arrays that operate interferometrically and hierarchically on multiple spatial scales. Examples of these multi-scale hierarchical aperture arrays include the Murchison Widefield Array \cite[MWA;][]{Tingay+2013}, the Low Frequency Array \cite[LOFAR;][]{vanHaarlem+2013}, the swarm of Long Wavelength Arrays \cite[LWA Swarm;][]{Dowell+2018}, and the Square Kilometre Array low \cite[SKA-low;][]{Dewdney+2009}. The specific spatial scales are the dimensions of the antenna, station (a grouping of antennas), and the array (a grouping of stations), denoted by $D_\textrm{a}$, $D_\textrm{s}$, and $D_\textrm{A}$, respectively. The number of stations in the array and the number of antennas in a station (indexed by $m$) are denoted by $N_\textrm{s}$ and $N_{\textrm{a/s}_m}$, respectively. 
% Although $N_\textrm{a/s_m}$ could vary with each station, we assume it remains the same for each station for simplicity.

@@

\begin{figure}
% \includegraphics[width=\linewidth]{figures/flops_calc.pdf}
\includegraphics[width=\linewidth]{figures/flops_calc_abridged.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:hybrid-architectures-cost-schematic}}
\end{figure}
